Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2022-08-04 vertical-thermal-review.Rmd
misc updates

Martijn Slot^3^ (ORCID: 0000-0002-5558-1792; Twitter: @martijn_slot; Facebook: martijn.slot.52)

Ian R. McGregor^4^ (ORCID: 0000-0002-5763-021X; Twitter: @ecoterrestrian)

Elsa M. Ordway^2,5^ (ORCID: 0000-0002-7720-1754; Twitter: @ElsaOrdway)

@@

Thomas N. Buckley^8^ (ORCID: 0000-0001-7610-7136; Twitter: @TomBuckleyLab)

Kristina J. Anderson-Teixeira^1,3^* (Orcid ID : 0000-0001-8461-9713; Twitter: @K_A_Teixeira)

>>>>

Martijn Slot^3^ (ORCID: 0000-0002-5558-1792; Twitter: martijn_slot; Facebook: martijn.slot.52)

Ian R. McGregor^4^ (ORCID: 0000-0002-5763-021X; Twitter: ecoterrestrian)

Elsa M. Ordway^2,5^ (ORCID: 0000-0002-7720-1754; Twitter: ElsaOrdway)

@@

Thomas N. Buckley^8^ (ORCID: 0000-0001-7610-7136; Twitter: TomBuckleyLab)

Kristina J. Anderson-Teixeira^1,3^* (Orcid ID : 0000-0001-8461-9713; Twitter: K_A_Teixeira)
